\malg: a Novel Interest Management Algorithm for Distributed Simulations of MMOGs

### 2008-07-31 trunk/textos/dsrt/extremeieeeaoi.tex
CAPPING
ALMOST DONE---

@@

%CAPABLE !!!!
\textbf{Avatar} is the player's representation in the virtual environment. Through his avatar, a player interacts with the game world and with the other players. Examples of avatars are the characters in MMORPGs (massively multiplayer online role-playing games), like World of Warcraft \cite{worldofwarcraft}.

\textbf{Entities} are the constituent parts of the virtual world. Examples of entities are the avatars of the players as well as avatars controlled by artificial intelligence of the server - monsters of MMORPGs, for example - and objects in the environment, such as doors, weapons and items with which avatars can interact.

@@

\begin{itemize}
 \item Avatar's view angle, to determine which entities the player must be able to see because they are in front of his avatar and within the maximum view distance;  
 \item Close area, whose purpose is %evitar que ocorram problemas caso o jogador faça seu avatar girar ao redor do próprio eixo muito rapidamente, além de 
 to improve the game quality in the space near the avatar. Its radius is the critical distance;
 \item Update frequency attenuation.
\end{itemize}

@@

%------------------------------------------------------------------------- 
\Section{Conclusion}
\label{conclusion}
In this work, we presented the \malg\ interest management algorithm, whose main idea is to vary the state update frequency of the game entities according to their relevance to each client that will receive the updates. The \malg\ area of interest consists of a circular sector, corresponding to the player field of view, plus a smaller circle, which represents the area close to that player's avatar. The goal of this close area is to maintain the game state inside it the most up-to-date possible, in order to improve the game near the avatar. Joining these characteristics, we obtained an algorithm that achieved a significant reduction of the maximum upload bandwidth utilization by the server, which decreased 52.03\% and 33.10\%, compared to circle and field of view based interest management algorithms, respectively. The average upload bandwidth utilization by the server also decreased 63.51\% and 33.58\%, compared to the same algorithms.

@@

%------------------------------------------------------------------------- 
%\nocite{ex1,ex2}
\bibliographystyle{latex8}
\bibliography{dsrt}

>>>>

\newcommand{\squishlist}{
   \begin{list}{$\bullet$}
    { \setlength{\itemsep}{0pt}      \setlength{\parsep}{3pt}
      \setlength{\topsep}{3pt}       \setlength{\partopsep}{0pt}
      \setlength{\leftmargin}{1.5em} \setlength{\labelwidth}{1em}
      \setlength{\labelsep}{0.5em} } }

\newcommand{\squishlisttwo}{
   \begin{list}{$\bullet$}
    { \setlength{\itemsep}{0pt}    \setlength{\parsep}{0pt}
      \setlength{\topsep}{0pt}     \setlength{\partopsep}{0pt}
      \setlength{\leftmargin}{2em} \setlength{\labelwidth}{1.5em}
      \setlength{\labelsep}{0.5em} } }

\newcommand{\squishend}{
    \end{list}  }

@@

%CAPABLE !!!!
\textbf{Avatar} is the player's representation in the virtual environment. Through his avatar, a player interacts with the game world and with the other players.

\textbf{Entities} are the constituent parts of the virtual world. Examples of entities are the avatars of the players as well as avatars controlled by artificial intelligence of the server - monsters, for example - and objects in the environment, such as doors, weapons and items with which avatars can interact.

@@

\squishlist   %% \begin{itemize}
  \item Avatar's view angle, to determine which entities the player must be able to see because they are in front of his avatar and within the maximum view distance;  
  \item Close area, whose purpose is %evitar que ocorram problemas caso o jogador faça seu avatar girar ao redor do próprio eixo muito rapidamente, além de 
 to improve the game quality in the space near the avatar. Its radius is the critical distance;
  \item Update frequency attenuation.
\squishend    %% \end{itemize}

@@

%------------------------------------------------------------------------- 
\Section{Conclusion}
\label{conclusion}
In this work, we presented the \malg\ interest management algorithm, whose main idea is to vary the state update frequency of the game entities according to their relevance to each client that will receive the updates. The \malg\ area of interest consists of a circular sector, corresponding to the player field of view, plus a smaller circle, which represents the area close to that player's avatar. The goal of this close area is to maintain the game state inside it the most up-to-date possible, in order to improve the game near the avatar. Joining these characteristics, we obtained an algorithm that achieved a significant reduction of the maximum upload bandwidth utilization by the server, which decreased 52.03\% and 33.10\%, compared to circle and field of view based interest management algorithms, respectively. The average utilization also decreased, 63.51\% and 33.58\%.

@@

%------------------------------------------------------------------------- 
%\nocite{ex1,ex2}
\bibliographystyle{latex8}
\bibliography{extremedsrt}
